### 2023-01-27 ms/ms.tex
Pre Montpelier

\textbf{Correlations among climate axes force trade-offs in the
  magnitude and kind of tracking species can maintain.} It is well
known that the axes of global climate are not independent and that
they are not changing independently\supercite{Harris2014,IPCC2014},
and so we would na\ively expect species' relative tracking of climate
axes to show similar patterns. As we show in Figure \ref{pca},
principal components analysis of species' current and past climate
distributions, which we refer to as their climate space, shows strong
correlations across climate variables. Yet our index does not:
species' relative degree of tracking is both of much higher dimension
(the amount of variance explained by each principal component axis is
similar) and shows relatively less correlation across climates
axes. Thus while species' positions in climate space show strong
associations, species' relative tracking of their position in climate
space does not. This result suggests that the ecological and
evolutionary rules that determine species' climate relationships are
changing, explaining why species' traits and evolutionary history are
relatively poor predictors of species' niche tracking. That species
are simultaneously tracking some aspects of climate while overshooting
others (see above) results from species trading off different,
correlated aspects of their climatic niche requirements.

>>>>

\textbf{Correlations among climate axes force trade-offs in the
  magnitude and kind of tracking species can maintain.} It is well
known that the axes of global climate are not independent and that
they are not changing independently\supercite{Harris2014,IPCC2014},
and so we would na\i vely expect species' relative tracking of climate
axes to show similar patterns. As we show in Figure \ref{pca},
principal components analysis of species' current and past climate
distributions, which we refer to as their climate space, shows strong
correlations across climate variables. Yet our index does not:
species' relative degree of tracking is both of much higher dimension
(the amount of variance explained by each principal component axis is
similar) and shows relatively less correlation across climates
axes. Thus while species' positions in climate space show strong
associations, species' relative tracking of their position in climate
space does not. This result suggests that the ecological and
evolutionary rules that determine species' climate relationships are
changing, explaining why species' traits and evolutionary history are
relatively poor predictors of species' niche tracking. That species
are simultaneously tracking some aspects of climate while overshooting
others (see above) results from species trading off different,
correlated aspects of their climatic niche requirements.
